04_DESeq_sexes

### 2019-05-24 analysis/04_DESeq2_sexes.Rmd
setup for more contrasts

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- levels(a.colData$treatment)
group2 <- group1

a <- plottotalDEGs(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(dds.female_pituitary, "female pituitary")
c <- plottotalDEGs(dds.female_gonad, "female gonad")
d <- plottotalDEGs(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(dds.male_pituitary, "male pituitary")
f <- plottotalDEGs(dds.male_gondad, "male gonad")
```

```{r plottotalDEGs, eval = T}
plot_grid(a + theme(legend.position = "none"),
          b + theme(legend.position = "none"),
          c + theme(legend.position = "none"),
          d + theme(legend.position = "none"),
          e + theme(legend.position = "none"),
          f + theme(legend.position = "none"),
          nrow = 2) 
```

>>>>

```{r returntotalDEGs, eval = T}
#DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
#DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
#DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGss.male_pituitary <- returntotalDEGs(dds.male_pituitary)
#DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r plotDEGs, eval = T}
#a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
#c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
#d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGss.male_pituitary, "male pituitary")
#f <- plottotalDEGs(DEGs.male_gondad, "male gonad")
```

```{r plottotalDEGs, eval = T}
plot_grid(#a + theme(legend.position = "none"),
          b + theme(legend.position = "none"),
          #c + theme(legend.position = "none"),
          #d + theme(legend.position = "none"),
          e + theme(legend.position = "none"),
          #f + theme(legend.position = "none"),
          nrow = 2) 
```
